Streaming CityJSON datasets

### 2024-04-29 paper/main.tex
Fix 2-3 things
Clean the tex file

% KAO: Remove extra spacing
\author{
 Hugo Ledoux\textsuperscript{1}, Gina Stavropoulou\textsuperscript{1}, Balázs Dukai\textsuperscript{2}}

@@

% If the corresponding author is NOT the final author, always add a % space before the subsequent comma, i.e.
% first author name\textsuperscript{a,}\thanks{Corresponding author} , % second author name \textsuperscript{b}, etc.
% thanks to Niclas Borlin 05-05-2016
% information on the corresponding author should not be used any longer and has been commented out
% C. Heipke, Jan 03,2024

% the use of the information of commissions and working groups should not be used any longer and has been commented out
% C. Heipke, Sept. 20,2022
%\commission{XX, }{YY} %This field is optional. If filled, XX and YY should be replaced by adequate numbers. See https://www2.isprs.org/commissions/
%\workinggroup{XX/YY} %This field is optional.
%\icwg{}   %This field is optional.

@@

Only one dataset sees its size slightly increase by 4\% when serialised to a CityJSONSeq file: \emph{Rotterdam}.
One reason for this is that the size of the CityJSON file is rather small in the first place, and therefore the indices are not high values.
As an experiment, we have created around 125 synthetic CityJSON datasets containing buildings, and each building is represented as a simple cube randomly generated.
There are no attributes, no semantics, no textures/materials. 
Figure~\ref{fig:synthetic_compression} shows that, as the CityJSON filesize increases, the compression factor increases.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/synthetic_compression.pdf}
  \caption{Compression factor of CityJSONSeq files for different synthetic datasets containing only but simple cuboid buildings. ($\frac{size(CityJSON) - size(CityJSONSeq)}{size(CityJSON)}$)}%
\label{fig:synthetic_compression}
\end{figure}
The smallest file contains only 526 buildings and its compression factor is -2\% (thus CityJSONSeq has a larger filesize than that of CityJSON), while the largest file has \num{3960105} buildings, and a compression factor of 18\%.

@@

From a practitioners point-of-view, we should stress that CityJSONSeq can easily be processed with \emph{Unix pipes} (also called \emph{pipelines}).
Pipelines allow us to chain several processes together, the output of a process becomes the input of the next one, and so on. 
Given 2 processes, the 2nd one can usually start before the 1st one has finished processing all the data.
This means in practice that the processing of a dataset can be performed by writing several programs that perform only small/atomic tasks; this makes the development and maintenance of code simpler.
Moreover, it allows us to develop the different programs in different languages. 
The pipeline used for preparing the datasets for this paper was actually a mix of Python (the program `cjio' and `cjdb') and Rust (`cjseq'), and another program written in C++ could easy be added.

@@

% We developed CityJSONSeq mainly because we wanted to be able to stream large CityJSON files from a server.

% \begin{itemize}
%   % \item We have kept most of the structure of CityJSON so that parsers do not need to be adapted much.
%   % \item CityJSONSeq is an attractive alternative to CityJSON, in most uses it is better to use since it is compacter, processing it uses less memory and is faster.
%   \item it opens up many possibilities for processing large 3dcm by using Unix pipes. A few of the tools developed for CityJSON are already reading/writing to stdin/stdout, so they can be chained together.
%   \item cjseqview, cjseqval are two of them, but developing others to eg filter, calculate volumes or repair geometries would be trivial
%   \item the nice part is that the tools do not need to be written in the same language, one pipeline can have tools built in Python and Rust and C++ and it all works nicely.
%   \item extensions: these should be placed in the metadata or collection
% \end{itemize}

% Disadvantages:
% \begin{itemize}
%   \item  Software implementing CityJSON need to account for both regular CityJSON and CityJSONSeq.
%   \item  In case of many, small, interconnecting CityObjects, a global vertex list would provide better compression than the separate vertex lists of the CityJSONFeatures.
%   \item  Appearances (esp. Material) are relatively heavy objects with many properties. If an appearance is shared across most CityObjects, duplicating it in each Feature could negate the effect of small vertex indices and actually increase the filesize compared to a regular CityJSON file. This is just theorizing, haven't tested.
% \end{itemize}

{
	\begin{spacing}{1.17}
		\normalsize
		\bibliography{refs} % Include your own bibliography (*.bib), style is given in isprs.cls
	\end{spacing}
}

>>>>

% KAO: Remove extra spacing
\author{
 Hugo Ledoux\textsuperscript{1}\thanks{corresponding author}, Gina Stavropoulou\textsuperscript{1}, Balázs Dukai\textsuperscript{2}}

@@

@@

Only one dataset sees its size slightly increase by 4\% when serialised to a CityJSONSeq file: \emph{Rotterdam}.
One reason for this is that the size of the CityJSON file is rather small in the first place, and therefore the indices are not high values.
As an experiment, we have created around 125 synthetic CityJSON datasets containing buildings, and each building is represented as a simple cube randomly generated.
There are no attributes, no semantics, no textures/materials. 
Figure~\ref{fig:synthetic_compression} shows that, as the CityJSON filesize increases, the compression factor increases.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/synthetic_compression.pdf}
  \caption{Compression factor of CityJSONSeq files for different synthetic datasets containing only but simple cuboid buildings.}%
\label{fig:synthetic_compression}
\end{figure}
The smallest file contains only 526 buildings and its compression factor is -2\% (thus CityJSONSeq has a larger filesize than that of CityJSON), while the largest file has \num{3960105} buildings, and a compression factor of 18\%.

@@

From a practitioners point-of-view, we should stress that CityJSONSeq can easily be processed with \emph{Unix pipes} (also called \emph{pipelines}).
Pipelines allow us to chain several processes together, the output of a process becomes the input of the next one, and so on. 
Given 2 processes, the 2nd one can usually start before the 1st one has finished processing all the data.
This means that, in practice, the processing of a dataset can be performed by writing several programs that perform a few small/atomic tasks; this makes the development and maintenance of code simpler.
Moreover, it allows us to write the code in different languages. 
The pipeline used for preparing the datasets used in this paper was actually a mix of Python (the program `cjio' and `cjdb') and Rust (`cjseq'), and another program written in C++ could easy be added.

@@

\newpage
{
	\begin{spacing}{1.17}
		\normalsize
		\bibliography{refs} % Include your own bibliography (*.bib), style is given in isprs.cls
	\end{spacing}
}
